---
title: "covid 19"
author: "Cadence Gorden"
date: "09/27/22"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```

```{r eval=FALSE}
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))
```

### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex


To find out if dying is independent of sex we will be using graphical, numerical, and infertial tests. 

Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```

  
The graphical results shows us that men died off more than women. 




  
## Numerical results
```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

The numerical results her show us that the men are dying off more than two time the rate of the women.

## Inferential results 




## Conclusions

